### 2021-11-23 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@4600018fd816aa1cdba8869d842be49bb0922f9b 🚀

The final chapter consists of a collection of modules in the Julia
language for different aspects of community ecology, including most of
the code used for the preceding chapters. Indeed
\texttt{MetacommunityDynamics.jl} (MCD.jl) is the epicenter of this set
of tools, but due to the nature of the Julia language, MCD.jl is
interoperable with serveral existing packages within the
\texttt{EcoJulia} organization, including several to which I have
contributed. A diagram showing the relation between these packages is
shown in fig.~\ref{fig:software}.

We need tools to generate synthetic data from a \emph{known} set of
mechanisms and parameters to test our methods for parameter inference
and forecasting on this \emph{known} system to assess the effectiveness
of these inference and forecasting methods.

@@

\texttt{MetacommunityDynamics.jl} is built on \texttt{DynamicGrids.jl},
a library for high-performance gridded simulations in the \texttt{Julia}
language, and Dispersal.jl (Maino \emph{et al.} 2021), and extension of
\texttt{DynamicGrids.jl} specifically for modeling organism dispersal.
It also contains integrations with \texttt{EcologicalNetworks.jl}
(Poisot \emph{et al.} 2019) to generate metawebs, or can use empirical
networks from Mangal.jl (Banville \emph{et al.} 2021).

It implements the general framework for community dynamics proposed by
(\textbf{Velland2010ConSyn?}), where all community processes can divided
into four categories: selection, dispersal, drift, and speciation.

@@

The software as it exists is capable of simulating the biomass dynamics
of arbitrarily large food-webs using Lotka-Volterra, Holling Type-II, or
Holling Type-III functional responses. It currently has methods to
implement Gaussian drift, and verious forms of dispersal via
Dispersal.jl. Also occupancy dynamics for Levins metapopulations
(\textbf{levins1967?}), and spatially explicit Hanski metapopulatoins
(\textbf{hanski2001?}). This is most of what needs to exist for the
preceding chapters. In-progress functionality includes selection (which
affects growth-rate) on arbitrary environmental variables in progress,
as well as traits.

@@

>>>>

The final chapter consists of a collection of modules in the Julia
language for different aspects of community ecology, including most of
the code used for the preceding chapters. Indeed
\texttt{MetacommunityDynamics.jl} (MCD.jl) is the epicenter of this set
of tools, but due to the nature of the Julia language, MCD.jl is
interoperable with serveral existing packages within the
\texttt{EcoJulia} organization, including several to which I have
contributed. We need a software library like this to generate synthetic
data from a \emph{known} set of mechanisms and parameters to test our
methods for parameter inference and forecasting on this \emph{known}
system to assess the effectiveness of these inference and forecasting
methods.

@@

A diagram showing the relation between these packages is shown in
fig.~\ref{fig:software}. \texttt{MetacommunityDynamics.jl} is built on
\texttt{DynamicGrids.jl}, a library for high-performance gridded
simulations in the \texttt{Julia} language, and Dispersal.jl (Maino
\emph{et al.} 2021), and extension of \texttt{DynamicGrids.jl}
specifically for modeling organism dispersal. It also contains
integrations with \texttt{EcologicalNetworks.jl} (Poisot \emph{et al.}
2019) to generate metawebs, or can use empirical networks from Mangal.jl
(Banville \emph{et al.} 2021). It implements the general framework for
community dynamics proposed by (\textbf{Velland2010ConSyn?}), where all
community processes can divided into four categories: selection,
dispersal, drift, and speciation.

@@

The software as it exists is capable of simulating the biomass dynamics
of arbitrarily large food-webs using Lotka-Volterra, Holling Type-II, or
Holling Type-III functional responses. It currently has methods to
implement Gaussian drift, and verious forms of dispersal via
Dispersal.jl. Also occupancy dynamics for Levins metapopulations (Levins
1969), and spatially explicit Hanski-Ovaskainen metapopulations (Hanski
\& Ovaskainen 2000; Ovaskainen \emph{et al.} 2002). This is most of what
needs to exist for the preceding chapters. In-progress functionality
includes selection (which affects growth-rate) on arbitrary
environmental variables in progress, as well as traits.

@@

\leavevmode\hypertarget{ref-Levins1969DemGen}{}%
Levins, R. (1969). Some Demographic and Genetic Consequences of
Environmental Heterogeneity for Biological Control. \emph{Bulletin of
the Entomological Society of America}, 15, 237--240.
